\TheTitle

### 2015-08-17 linvis.tex
Design: Use-cases
Adding use-cases
Flipping design and implementation details sections.

In this paper, we present the design decisions behind a web-based tool built
around a tree-based model instead of the DAG. We demonstrate the advantages of
this model over the use of the DAG. Our tool provides information about the
location of a given commit in the respective merge tree, the files edited, the
modules edited, and the commit message in a given commit or merge. The tool
allows users to apply various filters, including the release, a keyword or
phrase from the log preview, the name of the author, or the commit id. The user
can request all the top-level merges containing a commit or merge that matches
the query, or all commits and merges that match the query.

@@

Core Model:
	Merges are inner nodes
	Commits are leaf nodes

@@

The goal is to build a tool that make navigation of the kernel commit
information simpler, while providing an explanation of the changes occurring at
each commit and merge. Part of making the information usable is to narrow the
results down into only the information that is relevant to what the user is
looking for.

>>>>

In this paper, we present the design decisions behind a web-based tool built
around a tree-based model instead of the DAG.

We demonstrate the advantages of this model over the DAG two main use-cases.
Our tool provides information about the location of a given commit in the
respective merge tree, the files edited, the modules edited, and the commit
message in a given commit or merge. The tool allows users to apply various
filters, including the release, a keyword or phrase from the log preview, the
name of the author, or the commit id. The user can request all the top-level
merges containing a commit or merge that matches the query, or all commits and
merges that match the query.

@@

@@

The goal is to build a tool that make navigation of the kernel commit
information simpler, while providing an explanation of the changes occurring at
each commit and merge. Part of making the information usable is to narrow the
results down into only the information that is relevant to what the user is
looking for. We designed the tool with two use-cases in mind, though a user may
switch roles many times as they work.

\textit{Use-case 1: top-to-bottom approach}\\
These are users that are maintaining a section of the kernel and would like to
pick a merge from the future merges and merge it directly into their current
repository. This is useful for minimizing required implementation on the side
of the maintainer. We must provide them with methods of navigating from a more
general set of merges toward a specific set of merges and commits.

\textit{Use-case 2: bottom-to-top approach}\\
These are users that know what merge or commit they are working with and would
like to see what else is happening around their current commit. This is useful
to see how changes to a given file will break other changes made by other
commits. This is primarily for maintainers that have to perform some
implementation work in order to correctly merge the patches from the future.
These users may also know what module(s) they are dealing with, and are looking
for modules that are relevant to the area they are working on. We must provide
them methods of navigating from a specific commit to a more general merge,
allowing them to see a bigger picture.
